\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 draft.tex
save space in sec 4 and 5

The \emph{BugFinder component} randomly generates pairs of lists. The lists in a
pair are permutations of each other. A concrete counterexample is reported if
inputting any pair of lists from the generated ones to the reducer generates
different results. Our procedure for generating random pairs is quite naive. We
use five different input list of lengths 5, 7, 9, 11, and 13. For each length,
we generate 300 lists and pick uniformly at random one of its permutations.
Although the approach is simple; in practice, it finds counterexamples in all of
our non-commutative benchmarks in a few seconds.

@@

%=============================================================================
\subsection{The Prover: Reduce Commutativity Checking to SMT Solving}
\label{sec:prover}
%=============================================================================

@@

%-----------------------------------------------------------------------------
\paragraph{A note on dealing with output in the main loop.} 
%-----------------------------------------------------------------------------

@@

%=============================================================================
\subsection{An Optimisation by Live Variable Analysis}
\label{section:optimizations}
%=============================================================================

@@

To handle the above issue, we perform a simple backward live variable analysis
to collect all variables whose value may propagate to the output command after
the loop execution. Only these variables are then required to be equivalent. In
our evaluation, the ratio of reducers that our approach can successfully analyse
is significantly increased---in particular, from $6.8~\%$ to $97.5~\%$---by
using this optimisation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evaluation} \label{section:exp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%-----------------------------------------------------------------------------
\paragraph*{Benchmark collection} 
%-----------------------------------------------------------------------------

@@

%-----------------------------------------------------------------------------
\paragraph*{Results} 
%-----------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{splncs-sorted}
\bibliography{refs}

>>>>

The \emph{BugFinder component} randomly generates pairs of lists. The lists in a
pair are permutations of each other. A concrete counterexample is reported if
inputting any pair of lists from the generated ones to the reducer generates
different results. Our procedure for generating random pairs is quite naive. We
use five different input list of lengths 5, 7, 9, 11, and 13. For each length,
we generate 100 lists and pick uniformly at random one of its permutations.
Although the approach is simple; in practice, it finds counterexamples in all of
our non-commutative benchmarks in a few seconds.

@@

%=============================================================================
\vspace{-2mm}
\subsection{The Prover: Reduce Commutativity Checking to SMT Solving}
\vspace{-2mm}
\label{sec:prover}
%=============================================================================

@@

%-----------------------------------------------------------------------------

\paragraph{A note on dealing with output in the main loop.} 
%-----------------------------------------------------------------------------

@@

%=============================================================================
\vspace{-2mm}
\subsection{An Optimisation by Live Variable Analysis}
\vspace{-2mm}
\label{section:optimizations}
%=============================================================================

@@

To handle the above issue, we perform a simple backward live variable analysis
to collect all variables whose value may propagate to the output command after
the loop execution. Only these variables are then required to be equivalent. For the example above, the variable $t$ will be ignored in the equivalence checking and hence the program can be proven commutative. In
our evaluation, the ratio of reducers that our approach can successfully analyse
is significantly increased---in particular, from $6.8~\%$ to $97.5~\%$---by
using this optimisation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3mm}
\section{Evaluation} \label{section:exp}
\vspace{-2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%-----------------------------------------------------------------------------
\vspace{-1mm}
\paragraph*{Benchmark collection} 
%-----------------------------------------------------------------------------

@@

%-----------------------------------------------------------------------------
\vspace{-1mm}
\paragraph*{Results} 
%-----------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\bibliographystyle{splncs-sorted}
\bibliography{refs}
